% Note: Requires Deedy Resume Package (deedy-resume.cls)
\title{Brian Quinn – Professional Resume}
\documentclass[letterpaper]{deedy-resume}
\usepackage{hyperref}
\usepackage{color}
\usepackage[document]{ragged2e}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\begin{flushleft}
\Huge \center \textbf{Brian James Quinn}\\*
\begin{small}
\color{darkgray} \textbf{Github:} \color{gray} \url{github.com/brianjamesquinn1} | \url{github.com/blobmasterbrian}
\vspace{-7mm}
\textbf{\urlstyle{same}{\footnotesize \\ \url{}} \href{mailto:brianjamesquinn1@gmail.com}{\underline} brianjamesquinn1@gmail.com | +1 (406) 407-2294}
\end{small}
\end{flushleft}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.31\textwidth} 

\section{Education} 
\subsection{New York University}
\descript{B.S. Computer Science}
\location{Polytechnic School of Engineering}
\sectionspace

\section{Integrations}
\subsection{Third Party Integrations}
\descript{\small Payment Processors}
Stripe \\
Braintree \\
Modern Treasury \\
ACHQ \\
SVB \\
Orum \\
\sectionspace

\descript{\small Verification Providers}
Plaid \\
\sectionspace

\descript{\small Loan Origination/Management Systems}
Loanpro \\
Digifi \\
\sectionspace

\descript{\small Lending Marketplaces}
LendingTree \\
MyAutoLoan \\
Solera \\
Westlake \\
\sectionspace

\section{Skills}
\subsection{Programming}
\descript{\small Languages \qquad Technologies}
\begin{tabbing}
Go ~~~~~~~~~~~~~~~~~~~~~~~~ \=Serverless \\
TS/JS                       \> Docker \\
C/C++                       \> Kubernetes \\
Java                        \> PubSub \\
Python                      \> Redis \\
SQL                         \> AWS/GCP \\
\end{tabbing}

\end{minipage} 
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.68\textwidth} 



\section{Experience}
\runsubsection{Tenet} |\descript{\small Director of Engineering / Staff Software Engineer}
\location{Remote}
\vspace{\topsep}
\begin{tightitemize}
\item Rearchitected all data models in the database starting day 1 of joining the company. \\
\item Designed the architecture of the entire platform, separating technological services to reflect their business domains. \\
\item Derisked the company from existential failure by interfacing our integrations. This allowed me to migrate our entire banking infrastructure over a single weekend during the SVB collapse resulting in 0 downtime for servicing loans and payments. \\
\item Delivered key partnerships that were critical to the successful funding of our Series A. \\
\item Implemented process on the executive level to increase company efficiency/outcomes. Created PRD, vendor analysis, etc templates to make data driven decisions about what projects to pursue. \\
\item Led the engineering organization to deliver on key objectives required to secure a partnership with the US Department of Energy. \\

\end{tightitemize}
\sectionspace 

\runsubsection{Bread} |\descript{\small Senior Software Engineer – Payments}
\location{Remote}
\vspace{\topsep}
\begin{tightitemize}
\item Designed and built a microservice that processes all payments through the Bread platform (roughly \$1 million worth of payments per day). \\
\item Integrated multiple third party providers to verify bank information and provide multiple different ways to process payments (Braintree, Stripe, Flinks, Giact, RBC, SVB, NACHA). \\
\item Collaborated cross-functionally to provide an API to process payments across multiple other microservices. \\
\item Primary owner/designer/programmer of multiple other microservices: payments, payments\_jobs, debt\_consolidation, debt\_consolidation\_jobs, collections, collections\_jobs, airflow\_dags. \\
\item Engineered multiple successful A/B test experiments driving revenue through increasing conversion rates. \\
\item Implemented texting functionality throughout our system which drove a 9\% increase in take rate along with a 12\% increase in conversion rate. Results were statistically significant. (p-value < .01) \\
\item Company sold for \textasciitilde{}1/2 billion dollars. \\

\end{tightitemize}
\sectionspace 

\runsubsection{Dailymotion} |\descript{\small Software Engineer}
\location{New York, NY}
%\vspace{\topsep}
\begin{tightitemize}
\item Developed features on a distributed adserver which runs a networked auction in 200 ms. \\
\item Redesigned, refactored, developed, and maintained the infrastructure for the automation framework. \\


\end{tightitemize}
\sectionspace 

\runsubsection{Amazon Web Services} |\descript{\small Software Development Engineer Intern}
\location{Seattle, WA}
\begin{tightitemize}
\item Processed/moved petabytes of archive data from the Glacier architecture onto S3 via a multithreaded process. \\
\item Verified the integrity of the moved data, queued failures for retry, and tracked performance metrics via a subsequent multithreaded process. \\
\end{tightitemize}
\sectionspace 

\end{minipage}

\end{document}
